Power and Pitfalls of Generic Smart Contracts

### 2021-06-28 020_shared_entities_with_generics.tex

\begin{tcolorbox}
  \begin{center}\emph{Consistency of Shareholders}\end{center}
  If \<sse> is a {\codesize\texttt{SharedEntity<S,O>}}
  then the elements in the list \<sse.getShareholders()> have type \<S>.
\end{tcolorbox}

>>>>

\begin{tcolorbox}
  \begin{center}\emph{Consistency of Shareholders}\end{center}
  If \<sse> is a {\codesize\texttt{SharedEntity<S,O>}}
  then the elements contained in the list \<sse.getShareholders()> have type \<S>.
\end{tcolorbox}
